Usage metrics

### 2020-12-16 analysis/usage.Rmd
Fix paths

The setup chunk has a variable `jan` with setting to run the script on
docker on Jan's machine. This should be removed.

@@

C_raw -> C
corpus_size <- nrow(P)

overview_table(
  r("Corpus",corpus_size)
) 
```

@@

The data set has `r nrow(E)`distinct calls to the `eval` and its variants. 
There are `r length(unique(E$ev_package))` corpus packages with `eval` calls
(note that we may not trigger all `eval`s in a package due to spotty covereage).

@@

trig_evalq <- sites_per_variant %>% filter(ev_variant == "evalq")
trig_evalq <- if(nrow(trig_evalq) == 0)
{
  0
} else
{
  trig_evalq$n
}
trig_eval.parent <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
trig_eval.parent <- if(nrow(trig_eval.parent) == 0)
{
  0
} else
{
  trig_eval.parent$n
}
trig_local <- sites_per_variant %>% filter(ev_variant == "local") %>% .$n
trig_local <- if(nrow(trig_local) == 0)
{
  0
} else
{
  trig_local$n
}

>>>>

@@

C_raw -> C
corpus_size <- nrow(P)
overview_table(
  r("Corpus",corpus_size)
) 
```

@@

The data set has `r nrow(E)` distinct calls to the `eval` and its variants. 
There are `r length(unique(E$ev_package))` corpus packages with `eval` calls
(note that we may not trigger all `eval`s in a package due to spotty coverage).

@@

trig_evalq <- sites_per_variant %>% filter(ev_variant == "evalq")
trig_evalq <- if(nrow(trig_evalq) == 0)
{
  0
} else
{
  trig_evalq$n
}
trig_eval.parent <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
trig_eval.parent <- if(nrow(trig_eval.parent) == 0)
{
  0
} else
{
  trig_eval.parent$n
}
trig_local <- sites_per_variant %>% filter(ev_variant == "local")
trig_local <- if(nrow(trig_local) == 0)
{
  0
} else
{
  trig_local$n
}
